Checkpoint 3

### 2020-04-23 Checkpoint3.Rmd
Adding visualizations

###Demographic 
```{r}
#Demographic: Identification 
Finaldata <- data.frame(Finaldata) %>% mutate(state = State)
plot_usmap(data = Finaldata, values = "percent_white", color = "white") + 
  scale_fill_continuous(name = "Percent White", label = scales::comma) + 
  theme(legend.position = "right")+ ggtitle("Percent of Residents that Identify as White") + 
  theme(
plot.title = element_text(color="Black", size=14, face="bold")
)

@@

@@

#Analysis

```{r}
# Take a sub-sample of the data
set.seed(84735)
test1 <- Finaldata %>% 
  select(mean_KungFluInterest, percent_republican2016, percent_asian, StateColor) %>%
  na.omit() %>% 
  sample_n(500)

@@

```{r}
prediction_summary_data <- function(y, yrep, prob_inner = 0.5, prob_outer = 0.95){
  # Calculate summary statistics of simulated 
  # posterior predictive models for each case
  l_outer <- function(x){quantile(x, (1-prob_outer) / 2)}
  l_inner <- function(x){quantile(x, (1-prob_inner) / 2)}
  u_inner <- function(x){quantile(x, 1 - (1-prob_inner) / 2)}
  u_outer <- function(x){quantile(x, 1 - (1-prob_outer) / 2)}
  df <- data.frame(yrep) %>% 
    summarize_all(list(mean, sd, median, mad, l_outer, l_inner, u_inner, u_outer)) %>%
    unlist() %>% 
    matrix(., length(y), 8) %>% 
    data.frame()
  names(df) <- c("post_mean", "post_sd", "post_median", "post_mad", "l_outer", "l_inner", "u_inner", "u_outer")
  data.frame(cbind(y, df))
}

>>>>

### Demographic 
```{r}
#Demographic: Identification 
Finaldata <- data.frame(Finaldata) %>% mutate(state = State)
plot_usmap(data = Finaldata, values = "percent_white", color = "white") + 
  scale_fill_continuous(name = "Percent White", label = scales::comma) + 
  theme(legend.position = "right")+ ggtitle("Percent of Residents that Identify as White") + 
  theme(
plot.title = element_text(color="Black", size=14, face="bold")
)

@@

### COVID-19 Cases

```{r}
## Creating a df of just the cases the week before 3/17
weekbefore <- data.frame(states_cases_data) %>% filter(date <= as.Date("2020-03-17"))

plot1<- plot_usmap(data = weekbefore, values = "positive", color = "white") + 
  scale_fill_continuous(name = "Cases", label = scales::comma) + 
  theme(legend.position = "right")+ ggtitle("# of COVID Cases Before 3/17") + 
  theme(
plot.title = element_text(color="Black", size=8)
)

## Creating a df of just the cases the week after 3/17
weekafter <- data.frame(states_cases_data) %>% filter(date >= as.Date("2020-03-17"))

plot2<-plot_usmap(data = weekafter, values = "positive", color = "white") + 
  scale_fill_continuous(name = "Cases", label = scales::comma) + 
  theme(legend.position = "right")+ ggtitle("# of COVID Cases After 3/17") + 
  theme(
plot.title = element_text(color="Black", size=5)
)

# The number of Positive Covid Cases, comparison before and after the China Virus announcement 
grid.arrange(plot1, plot2, ncol=2)
```

```{r}
# 
ggplot(Finaldata, aes(x = positive, fill = StateColor)) + 
    geom_density(alpha = .8)+ ggtitle("Positive COVID-19 Cases by State Party") + xlab("Cases") + ylab("Density")+xlim(0,500)
```

```{r}
library(statebins)
plot3<-statebins(state_data = weekbefore, state_col = "state",
                     text_color = "white", value_col = "positive",
                     brewer_pal="Spectral", font_size = 2,breaks =7,
                     legend_title="Week Before",
                 labels = c("0","1-5","5-10","10-20","20-30","30-40","50-100"))

### Drastic scale change, needs work for comparison sake
plot4<-statebins(state_data = weekafter, state_col = "state",
                     text_color = "white", value_col = "positive",
                     brewer_pal="Spectral", font_size = 3,breaks =6,
                     legend_title="Week After",labels = c("1-100", "100-500", "500-5000", "5000-15000", "15000-25000", "25000-35000"))

plot3
plot4
```

@@

# Analysis

```{r}
set.seed(84735)
test1 <- Finaldata %>% 
  select(mean_KungFluInterest, percent_republican2016, percent_asian, StateColor) %>%
  na.omit() %>% 
  sample_n(500)

@@

```{r, include=FALSE}
prediction_summary_data <- function(y, yrep, prob_inner = 0.5, prob_outer = 0.95){
  # Calculate summary statistics of simulated 
  # posterior predictive models for each case
  l_outer <- function(x){quantile(x, (1-prob_outer) / 2)}
  l_inner <- function(x){quantile(x, (1-prob_inner) / 2)}
  u_inner <- function(x){quantile(x, 1 - (1-prob_inner) / 2)}
  u_outer <- function(x){quantile(x, 1 - (1-prob_outer) / 2)}
  df <- data.frame(yrep) %>% 
    summarize_all(list(mean, sd, median, mad, l_outer, l_inner, u_inner, u_outer)) %>%
    unlist() %>% 
    matrix(., length(y), 8) %>% 
    data.frame()
  names(df) <- c("post_mean", "post_sd", "post_median", "post_mad", "l_outer", "l_inner", "u_inner", "u_outer")
  data.frame(cbind(y, df))
}
